Interpretable Neural Networks using EAGGA

### 2025-03-13 paper/main.tex
add bullets on evaluation of Pareto front estimates + reference for crowding distance intuition

@@

    % TODO: reference?

>>>>

(evaluation)
- if knowledge over true Pareto-front, evaluating set of individuals can be done based on distance of estimated to true Pareto front
- if no knowledge over true Pareto-front, volume-based approaches are popular, which measure volume between Pareto front estim and some chosen
  reference point (usually worst point in objective space)
- \citep[pp. 8-10]{10.1145/3610536}

@@

    - \citep[p. 185, pp. 189-192]{genetic_algos}
